---
title: "Guide technique 2022"
subtitle: "Une manche de la Coupe des Nations Junior"
author: "Tour de l'Abitibi"
date: "11 au 17 juillet 2022"
output: 
  pagedreport::paged_windmill:
    front_img: "https://i.pinimg.com/564x/ef/75/5b/ef755b9dbfd816488773c33be1b2f6cc.jpg"
    logo: "img/logo/Tour_Logo.png"
    img_to_dark: TRUE
    logo_to_white: FALSE
    toc: TRUE
knit: pagedown::chrome_print
toc-title: "Table des Matières"
main-color: "#00424F"
params:
  annee: 2022
  ville: "Amos"
  langue: "FR"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)


library(kableExtra)
library(tidyverse)
library(pagedreport)
library(here)
library(readxl) 
library(formattable)

#setwd("C:/Users/Bruno/Dropbox/TourAbitibi/2022 Amos/Guide/R")
#here::i_am("_import_itineraire.R")

```

# Le mot du Maire pour `r params$annee` {.chapter}

`r readr::read_file("rmd/02_mots/mot_maire_FR.txt")`

\pagebreak

## Second level {.chapter}

This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.


This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

\pagebreak

### Itinéraire - Étape 1


```{r echo=FALSE}
Etape <- 1

calcul_iti_etape(Etape) %>% 
  kbl(col.names = NULL) %>%
  kable_minimal("striped",full_width = T, font_size = 12) %>%
  add_header_above(c("restant" , "fait" , "parcours" ,
                     iti_etape$Details$Descr_km[Etape],
                     paste(speed$kmh_rapide[Etape], " km/h"),
                     paste(speed$kmh_moy[Etape], " km/h"),
                     paste(speed$kmh_lent[Etape], " km/h") )) %>% 
  add_header_above(c( "KM"  = 2, "Info", iti_etape$Details$Descr_Villes[Etape]  , "Vitesse" = 3 ))
```



\pagebreak


### Un peu plus de texte



Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!

Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!

Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!

## Second level {.page-break-before}

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message! This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

## Second level {.chapter}

Finally, be sure to remove this message!
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.
Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!
This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.
This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

# And now part 2 {.chapter}

This file is what a user will see when they select your template. Make sure that you update the fields in the yaml header. In particular you will want to update the `output` field to whatever format your template requires.

## Second level {-}

This is a good place to demonstrate special features that your template provides. Ideally it should knit out-of-the-box, or at least contain clear instructions as to what needs changing.

Finally, be sure to remove this message!

